We are not the 99 percent: quantifying bright satellite distributions in the Local Group

### 2017-11-02 paper/paper.tex
+1 paragraph

It

@@

>>>>

@@

After building the normalized variables with the simulated data we
perform  a Kolmogorov-Smirnov test with the null hypothesis of belongig
to a normal distribution with mean and standard deviation computed
from the mean and standard deviation from the data itself. 
We find that the distributions for $w$, $c/a$ and $b/a$ cannot reject
the null hypothesis. 
Only the distribution for $\mu$ corresponds to a
uniform distribution.

We then build a multivariate normal distribution for $$
